\large{Vipassana for Hackers} \\ \Huge{The Proposal} \\ \large\textit{Version 0.1}

### 2024-06-26 the-proposal/the-proposal.tex
include up to "specific aims"

@@

\subsection{Overall Objective}
\subsection{Specific Aims}

@@

EXAMPLE: \\
05:00 - Wake \\
05:30 - 1 hour meditation \\
06:30 - Breakfast \\
07:30 - Exercise \\
09:00 - 3 hours meditation \\
12:00 - Lunch \\
13:00 - 3 hours meditation \\
16:00 - Writing period \\
18:00 - Evening meal \\
19:00 - 1 hour meditation \\
21:00 - Sleep

>>>>

As far as quantitative measures, such as future EEG, MEG, and fMRI readings, are concerned,
this study hypothesizes that readings taken from subjects will progress toward readings
found in ``expert'' groups of previous studies.
\cite{https://doi.org/10.1073/pnas.0407401101,https://doi.org/10.1371/journal.pone.0073417}
See \textit{RESEARCH DESIGN AND METHODS, Expertise}.

However, both quantitative and qualitative measures will be used primarily for
initial discovery and exploration.
Since no other study of this kind has ever been run, it is not possible to meaningfully
predict outputs.
See \textit{RESEARCH DESIGN AND METHODS, Methodological Issues}.

@@

\subsection{Overall Objective}

As an ``ultralong'' longitudinal study of continuous practice,
the primary goal is open discovery.

Most pre-existing studies on meditation focus on narrow outputs of the
practitioners' meditation activity.
Qualitiative examples include effects on emotional regulation, negative self-belief,
depression, anxiety, and amygdala response outside of meditation.
\cite{https://doi.org/10.1093/scan/nss054,
  https://doi.org/10.1037/a0018441,
  https://doi.org/10.31231/osf.io/hzv65}
Quantiative examples include discovery of high-amplitude gamma synchrony during meditation,
higher Parietal-Occipital EEG gamma activity during NREM sleep,
Heart Rate (HR) and High-Frequency Heart Rate Variability (HF-HRV) as useful proxies for effort,
and meditation experience correlated to reduced Default Mode Network (DMN) activity.
\cite{https://doi.org/10.1073/pnas.0407401101,
  https://doi.org/10.1371/journal.pone.0073417,
  https://doi.org/10.1016/j.ijpsycho.2015.04.017,
  https://doi.org/10.1073/pnas.1112029108}

This ultralong study will, instead, examine all aspects of prolonged practice of
Vipassana meditation.
Qualitative outputs will begin after the first quarter of the study.
Quantitative outputs will emerge as long-term access to research equipment becomes available.

\subsection{Specific Aims}

The study will produce qualitative writing describing the research-subject's experience.

The study will produce quantitative measures, based on equipment availability.

The study will also act as a template study methodology for others to follow,
or for other researcher-subjects to join if the study proves successful in
uncovering new discoveries.

There has been limited, unprofessional writing on the topic of the dangers of meditation.
\cite{ingram2020mastering,https://doi.org/10.1080/03060497.1983.11084578}
Even though these writings focus on Christian ideals and meditative concepts
(such as ``The Dark Night of The Soul''),
which have no relationship to Vipassana meditation whatsoever,
they do arise in discussions of Vipassana meditation from time to time.
As a result, it is a specific aim of this study to determine if there are
psychological or physical dangers presented by prolonged meditation practice.

@@

EXAMPLE: \\
05:00 - Wake \\
05:30 - 1 hour meditation \\
06:30 - Breakfast \\
07:30 - Exercise \\
09:00 - 3 hours meditation \\
12:00 - Lunch \\
13:00 - 3 hours meditation \\
16:00 - Writing period \\
18:00 - Evening meal \\
19:00 - 1 hour meditation \\
21:00 - Sleep \\
